---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r setup, include = FALSE}
dir.create(file.path(tempdir(), "sims"))
knitr::opts_knit$set(root.dir = file.path(tempdir(), "sims"))
```
# simcases

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build Status](https://www.travis-ci.com/audrey-b/simcases.svg?token=LCuTqqVUfUECxm1xTQLb&branch=master)](https://www.travis-ci.com/audrey-b/simcases)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/r36uoa15oab7fofd/branch/master?svg=true)](https://ci.appveyor.com/project/audrey-b/simcases/branch/master)
[![Codecov test coverage](https://codecov.io/gh/audrey-b/simcases/branch/master/graph/badge.svg?token=BsckUvkTy8)](https://codecov.io/gh/audrey-b/simcases)
[![License: GPL3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.html)
[![CRAN status](https://www.r-pkg.org/badges/version/simcases)](https://cran.r-project.org/package=simcases)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/simcases)
<!-- badges: end -->

simcases is an R package to simplify the conduct of simulation studies across multiple cases/scenarios.

## Installation

To install the latest release version from [CRAN](https://cran.r-project.org)
```r
install.packages("simcases")
```

To install the latest development version from [GitHub](https://github.com/audrey-b/simcases)
```r
# install.packages("remotes")
remotes::install_github("audrey-b/simcases")
```

## Demonstration

First, define the likelihood, constants, parameters and other characteristics of the models to use for the simulations.

```{r}
library(simcases)
lik = "for(i in 1:10){
          a[i] ~ dnorm(mu, 1/sigma^2)}"
const = list(mu=0)
sigma1 = list(sigma=1)
sigma2 = list(sigma=2)
all = ".*"
a = "a"
```

Specify the models to use. The first row is a header and the following rows each describe a model.

```{r}
models = "code constants parameters monitor
          lik  const     sigma1     a
          lik  const     sigma2     a
          lik  const     sigma1     all
          lik  const     sigma2     all"
```

Simulate data. The results are written to files.

```{r}
set.seed(10)
smc_simulate(models = models,
                  nsims = 3,
                  exists = NA,
                  ask = FALSE)
```

Analyse data according to specific cases (scenarios).

```{r}
prior <- "sigma ~ dunif(0, 6)"
sigma <- "sigma"
models_analysis <- "code code.add monitor
                    lik  prior    sigma
                    lik  prior    sigma"
cases <- "sims models
           1    1
           2    1
           3    2
           4    2"
smc_analyse(models = models_analysis,
                     cases = cases,
                     mode = simanalyse::sma_set_mode("quick"))
```

Evaluate the performance of the models across the cases (scenarios)

```{r}
args = "parameters
         sigma1
         sigma1
         sigma2
         sigma2"
smc_evaluate(args, cases, monitor="sigma")
```
Have a look at the files created.

```{r}
files <- list.files(getwd(), recursive=TRUE, all.files=TRUE)
print(files)
```

Load one file.

```{r}
readRDS(file.path(getwd(), files[9]))
```

## Additional features

When a large number of models is used, it can be more convenient to specify models as data frames to facilitate query and manipulation. The example above may be reproduced as follows.

```{r}
models <- tibble::tribble(
  ~parameters, ~monitor,
  "sigma1", "a",
  "sigma2", "all"
  )
models <- tidyr::expand(models, parameters, monitor)
models$code <- "lik"
models$constants <- "const"
models

set.seed(10)
smc_simulate(models = models,
                  nsims = 3,
                  fun = identity,
                  exists = NA,
                  ask = FALSE)
```

## Contribution

Please report any [issues](https://github.com/audrey-b/simcases/issues).

[Pull requests](https://github.com/audrey-b/simcases/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/audrey-b/simcases/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
