---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# simcases

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build Status](https://www.travis-ci.com/audrey-b/simcases.svg?token=LCuTqqVUfUECxm1xTQLb&branch=master)](https://www.travis-ci.com/audrey-b/simcases)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/r36uoa15oab7fofd/branch/master?svg=true)](https://ci.appveyor.com/project/audrey-b/simcases/branch/master)
[![Codecov test coverage](https://codecov.io/gh/audrey-b/simcases/branch/master/graph/badge.svg?token=BsckUvkTy8)](https://codecov.io/gh/audrey-b/simcases)
[![License: GPL3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.html)
[![CRAN status](https://www.r-pkg.org/badges/version/simcases)](https://cran.r-project.org/package=simcases)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/simcases)
<!-- badges: end -->

simcases is an R package to simplify the conduct of simulation studies across multiple cases/scenarios.

## Installation

To install the latest release version from [CRAN](https://cran.r-project.org)
```r
install.packages("simcases")
```

To install the latest development version from [GitHub](https://github.com/audrey-b/simcases)
```r
# install.packages("remotes")
remotes::install_github("audrey-b/simcases")
```

## Demonstration
```{r}
library(simcases)
lik = "Y ~ dnorm(mu, 1/sigma^2)
        Z ~ dpois(lambda)"
const = nlist(mu=0)
params1 = nlist(sigma=1, lambda=1)
params2 = nlist(sigma=2, lambda=1)
monitor.Y = "Y"
monitor.all = ".*"

simcases_simulate("code constants parameters monitor",
                  "lik  const     params1    monitor.Y
                   lik  const     params2    monitor.Y
                   lik  const     params1    monitor.all
                   lik  const     params2    monitor.all")
```

## Contribution

Please report any [issues](https://github.com/audrey-b/simcases/issues).

[Pull requests](https://github.com/audrey-b/simcases/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/audrey-b/simcases/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
